Tables/Graphs for Article

### 2018-01-03 article/draft1.Rnw
added section numbers, reformatted example questions table

@@

\section*{Introduction}

@@

\section*{Related Work}

@@

\section*{Materials}

% Table of categorical predictors
\begin{table}[!htbp]
\centering
\begin{tabular}{|p{10cm}|}
  \hline
  Day of the week the question was posted \\ \hline
  Device category the question pertains to. Categories include: Android\/Other Phone, Apple Products, Camera, Electronics, Game Console, Home, Other, PC, Tablet, Vehicle \\ \hline
  Whether or not the question's text contains any end punctuation marks (. ? !) \\ \hline
  Whether or not the question's text is in all lower case \\ \hline
  Whether or not the question's title contains at least one word that is considered ``frequently used'' among answered questions. See Appendix for a complete list of these terms. \\ \hline
  Whether or not the question's title contains at least one word that is considered ``frequently used'' among unanswered question. See Appendix for a complete list of these terms. \\ \hline
  Whether or not the question's title ends in a question mark \\ \hline
  Whether or not the user edited or added information to the question's text sometime after posting it. \\ \hline
  Whether or not the user made an effort to solve the problem prior to asking the question. \\ \hline
\end{tabular}
\caption{Categorical predictors derived}
\label{table:categorical}
\end{table}

% Table of quantitative predictors
\begin{table}[!htbp]
\centering
\begin{tabular}{|p{10cm}|}
  \hline
  Average number of characters in each question's tags\\ \hline
  Average tag ``score'' for all of a question's tags. A tag score is defined as the proportion of times a tag appears in all of the data. Questions without tags were assigned a score of 0. \\ \hline
  Number of characters in the question's text \\ \hline
  Number of characters in the user-defined device name \\ \hline
  Ratio of the number of line breaks to the number of characters in the question's text \\ \hline
\end{tabular}
\caption{Continuous predictors derived}
\label{table:continuous}
\end{table}

@@

\section*{Methods}

@@

In each fold of cross-validation, the full model was built on the training set and used to generate predicted hazard ratios on the corresponding test set. To assess prediction performance, predicted hazard ratios were entered into separate Cox models as the single quantitative predictor with response times as the survival time. The resulting Nagelkerke's R-square statistic, concordance statistic, Somers' \textit{Dxy}, partial likelihood ratio and p-value, were assessed as indicators of the model's performance \cite{Chen}. Signficant results from this model would indicate high predictive accuracy. The partial likelihood ratio assessed is a ratio of the log partial likelihood function evaluated at the parameter estimates, equivalent to a goodness of fit measure of the model with all predictors, and the log partial likelihood function for the null model with no predictors and only the baseline hazard function, equivalent to a goodness of fit measure for the null model. The p-value for this statistic was calculated from the $Ichi^2$ distribution \cite{find}. Concordance statistics and Somers' \textit{Dxy} are a measure of the model's discriminative ability. Concordance is defined as the probability that for any two randomly chosen questions, the question with the shorter response time also has the higher predicted hazard ratio. Concordance statistics close to 1 indicate high discriminative ability, while statistics close to 0.5 indicate discordance, or random predictions. Somers' \textit{Dxy} is the difference between the model's concordance statistic and discordance, 0.5. A Somers' \textit{Dxy} statistic of 0 indicates random predictions, while a statistic equal to 1 indicates perfect predictions \cite{Harrell2015}. These metrics were computed for each iteration on every training and test set. Averages of metrics across training and test sets were evaluated. The final model was then fit to the full data and the same metrics were computed and compared.

@@

\section*{Results and Discussion}

@@

% Table of percentiles 
\begin{table}[!h]
\centering
\begin{tabular}{rlr}
  \hline
 Percent\\ Answered & Time (hrs) \\ 
  \hline
  25 & 0.88 \\ 
  50 & 9.16 \\ 
  55 & 18.38 \\ 
  58 & 33.71 \\ 
  60 & 59.47 \\ 
  64 & 683.19 \\ 
   \hline
\end{tabular}
\caption{Kaplan-Meier estimated quantiles of survival time}
\label{table:quantiles}
\end{table}

@@

% Univariate analysis results
\begin{table}[!htbp]
\centering
\caption{Univariate analysis results for continuous predictors, ordered by increasing p-values} 
\begin{tabular}{| p{5cm} | p{2.5cm} | p{2cm} |}
  \hline
  Predictor & Transformation & p-value \\ 
  \hline
  \multirow{ 3 }{ 5cm }{ Average frequency score of a question's tags }
  & Untransformed & 1.270620e-08 \\
  & Log + 1 & 1.186521e-08 \\
  & *Square root & 1.464184e-11 \\ \hline
  \multirow{ 3 }{ 5cm }{ Average number of characters in each question's tags }
  & Untransformed & 2.611529e-02 \\ 
  & *Log + 1 & 6.018542e-05 \\
  & Square root & 2.999917e-04 \\ \hline
  \multirow{ 3 }{ 5cm }{ Number of characters in a question's text }
  & Untransformed & 6.947221e-12 \\
  & *Log & 0.000000e+00 \\
  & Square root & 1.110223e-16 \\ \hline
  \multirow{ 3 }{ 5cm }{ Number of characters in the user-defined device title }
  & Untransformed & 6.530431e-03 \\
  & *Log + 1 & 1.912977e-05 \\
  & Square root & 2.291424e-04 \\ \hline
  \multirow{ 3 }{ 5cm }{ Ratio of the number of line breaks to the number of characters in a question's text } 
  & Untransformed & 1.398819e-07 \\
  & Log + 1 & 1.092952e-07 \\
  & *Square root & 1.148792e-11 \\ \hline
  \multicolumn{ 2 }{ |l| }{ *Day of the week the question was posted } & 7.867705e-04 \\ \hline
  \multicolumn{ 2 }{ |l| }{ *Device category } & 0.000000e+00 \\ \hline
  \multicolumn{ 2 }{ |p{7.5cm}| }{ *Whether or not the question's text contained at least one end punctuation mark } & 2.535394e-09 \\ \hline
  \multicolumn{2}{ |p{7.5cm}| }{ *Whether or not the question's text is in all lower case } & 1.540030e-07 \\ \hline
  \multicolumn{2}{| p{7.5cm}|}{ *Whether or not the question's title contains terms considered to be frequently used among answered questions } & 7.639738e-05 \\ \hline
  \multicolumn{2}{ |p{7.5cm}| }{ *Whether or not the question's title contains terms considered to be frequently used among answered questions } & 7.639738e-05 \\ \hline
  \multicolumn{2}{ |p{7.5cm}| }{ *Whether or not the question's title contains terms considered to be frequently used among unanswered questions } & 0.000000e+00 \\ \hline
  \multicolumn{2}{ |p{7.5cm}| }{ *Whether or not the question's title ended in a questionmark } & 1.142308e-12 \\ \hline
  \multicolumn{2}{ |p{7.5cm}| }{ *Whether or not the user edited or added information to the question's text sometime after posting it } & 2.547222e-07 \\ \hline
  \multicolumn{2}{ |p{7.5cm}| }{ *Whether or not the user had been a member for less than one day before the question was posted } & 0.000000e+00 \\ \hline
  \multicolumn{2}{ |p{7.5cm}| }{ *Whether or not the user made an effort to solve the problem on their own, prior to asking the question } & 3.164815e-05 \\ \hline
\end{tabular}
\label{table:univariate_results}
\end{table}

@@

% Splines
\begin{table}[!htbp]
\centering
\begin{tabular}{| p{5cm} | l | l |}
  \hline
  Predictor & K & AIC \\ 
  \hline
  \multirow{ 4 }{ 5cm }{ Log transformation of the number of characters in a question's text } 
  & 0 & 65862.83 \\ 
  & *5 & 65862.02 \\ 
  & 4 & 65863.35 \\ 
  & 3 & 65862.08 \\ 
  \hline
  \multirow{ 4 }{ 5 cm }{ Square root transformation of the ratio of the number of line breaks to the number of characters in a question's text }
  & 0 & 65890.28 \\ 
  & 5 & 65884.70 \\ 
  & 4 & 65882.98 \\ 
  & *3 & 65881.93 \\ 
  \hline
  \multirow{ 4 }{ 5 cm }{ Square root transformation of the average frequency ``score'' of a question's tags }
  & *0 & 65890.75 \\ 
  & 5 & 65891.69 \\ 
  & 4 & 65891.75 \\ 
  & 3 & 65892.35 \\ 
  \hline
  \multirow{ 4 }{ 5 cm }{ Log transformation of the number of characters in the user-defined device title + 1 }
  & 0 & 65918.06 \\ 
  & *5 & 65847.34 \\ 
  & 4 & 65880.89 \\ 
  & 3 & 65898.00 \\ 
  \hline
  \multirow{ 4 }{ 5 cm }{ Log transformation of the average number of characters in a question's tags + 1 }
  & 0 & 65920.24 \\ 
  & 5 & 65911.20 \\ 
  & *4 & 65910.81 \\ 
  & 3 & 65914.98 \\ 
   \hline
\end{tabular}
\caption{Determining the optimal k number of splines for each predictor} 
\label{table:splines}
\end{table}

@@

% Cross-validation metrics
\begin{table}[!htbp]
\centering
\begin{tabular}{| r | r | r | r | r  | r | r | r |}
  \hline
 & HR & LR & p-value & $R^2$ & \textit{Dxy} & Concordance \\ 
  \hline
  Training Sets & 2.015619 & 936.6705 & 0.0000 & 0.1400518 & 0.2691182 & 0.6345591 \\ 
  Test Sets & 1.975100 & 219.8065 & 0.0000 & 0.1400518 & 0.2579717 & 0.6289859 \\
  Full Data & 2.01843 & 1164.784 & 0.0000 & 0.1393817 & 0.2680962 & 0.6340481 \\ 
   \hline
\end{tabular}
\caption{Performance Metrics} 
\label{table:cv}
\end{table}

@@

% Final model on full data
\begin{table}[!htbp]
\centering
\caption{Coefficients for predictors in the final model} 
\begin{tabular}{|p{1.5cm}|p{6cm}|p{2.5cm}|p{2.5cm}|}
  \hline
 Variable &  Levels & Hazard Ratios & p-value \\ 
  \hline
  \multirow{ 9 }{ 2 cm }{ Device Category } & Apple Product & 0.93 & \multirow{ 9 }{ 1.5cm }{ <0.0001 }\\ 
  & Camera & -0.26 & \\ 
  & Electronics & -0.08 &\\ 
  & Game Console & 0.21 &\\ 
  & Home & 0.39 &\\ 
  & Other & -0.11 &\\ 
  & PC & 0.43 &\\ 
  & Tablet & -0.15 &\\ 
  & Vehicle & 0.38 &\\
  \hline
  & Whether or not the user had been a member for less than one day before the question was posted & -0.10 & 0.0048 \\
  \hline
  & Whether or not the question's title contains terms considered to be frequently used among unanswered questions & -0.27 & <0.0001 \\ 
  \hline
  & Whether or not the question's title contains terms considered to be frequently used among answered questions & 0.05 & 0.2235\\ 
  \hline
  & Whether or not the question's title ended in a questionmark & 0.25 & <0.0001\\ 
  \hline
  & Whether or not the question's text contained at least one end punctuation mark & 0.03 & 0.5348\\ 
  \hline
  & Whether or not the question's text is in all lower case & -0.18 & 0.0052 \\ 
  \hline
  & Whether or not the user edited or added information to the question's text sometime after posting it & 0.28 & 0.0009 \\ 
  \hline
  & Whether or not the user made an effort to solve the problem on their own, prior to asking the question & -0.09 & 0.0137 \\ 
  \hline
  \multirow{ 6 }{ 2 cm }{ Day of the Week } & Monday & 0.01 & \multirow{ 6 }{ 1.5cm }{ 0.0004 }\\ 
  & Saturday & -0.07 & \\ 
  & Sunday & -0.11 & \\ 
  & Thursday & 0.03 & \\ 
  & Tuesday & 0.09 & \\ 
  & Wednesday & 0.10 & \\ 
  \hline
  & Square root transformation of the average frequency ``score'' of a question's tags & 2.23 & 0.0020 \\ 
  \hline
  \multirow{ 3 }{ 2cm }{ Square root transformation of the average number of characters in a question's tags } & _ & -0.08 & 0.0457\\ 
  & avg\_tag\_length' & 0.58 & Nonlinear \\ 
  & avg\_tag\_length'' & -1.52 & 0.0804\\ 
  \hline
  \multirow{ 4 }{ 2cm }{Log transformation of the number of characters in a question's text} & text length & -0.08 & 0.4344
  & text\_length' & -0.36 & Nonlinear \\ 
  & text\_length'' & 2.39 & 0.4578 \\
  & text\_length''' & -3.69 & \\ 
  \hline
  \multirow{ 4 }{ 2cm }{ Square root transformation of the number of characters in a question's device title} & device length & -0.07 & 0.2790 \\
  & device\_length' & 0.18 & Nonlinear \\ 
  & device\_length'' & -0.27 & 0.4185\\ 
  & device\_length''' & 0.21 & \\ 
  \hline
  \multirow{ 2 }{ 2cm }{ Square root transformation of the ratio of number of line breaks to number of characters in a question's text} & line break & 0.12 & 0.3569 \\
  & newline\_ratio' & 0.36 & Nonlinear: 0.6191 \\ 
   \hline
\end{tabular} 
\label{table:coefficients}
\end{table}

@@

\section*{Conclusion}

@@

The data analyzed for this model presented limitations, and may explain the model's low predictive accuracy. Many users on the CQA incorrectly specified the device name in their question (e.g. ``Turtle Beach Ear Force Xmy grandson chewed through the wire while he was playing it's brand-new is there anyway I can have it fixed0 One''), or did not include a device name at all. Many users also incorrectly used the tagging system by including ambiguous and lengthy tags like ``someone sat on it :('' or ``help me please!!!!!''(tags are generally a couple key words that describe the topic of the question). These inconsistencies in the data presented some difficulties in analysis, and may explain the model's low R^2 and discrimination indexes.

@@

\section*{Acknowledgement}

@@

\section*{Appendix}

% -----------------------------------------------------------
\subsection*{Posted questions}

% answered question id = 397414
% unanswered question id = 399971
% Table to display questions
\begin{table}[!htbp]
\centering
\begin{tabular}{| p{2cm} | p{2cm} | p{3cm} | p{6cm} | {2cm} | {2cm} | {2cm} | {2cm} |}
  \hline
 Answered & Device & Title & Text & New User? & Date Posted & First Answer Date & Response Time \\
  \hline
  Yes & iPhone 6 & iPhone water damage, touch screen issue & So I dropped my iPhone in water 4 days ago. Have done the whole rice thing and seen huge difference in it. However, only one side of my screen works and it is the one side which I need to unlock the phone. What would be the best way forward? & Yes & 2017-05-10 21:50:48 GMT & 2017-05-10 23:12:27 & 1.361 hr \\ \hline
  No & android tablet & ccccaaaan you help me fix my touch screen & touch screen not worki & No & 2017-05-23 07:35:12 GMT & NA & NA \\
   \hline
\end{tabular}
\caption{Answered and unanswered questions}
\label{table:questions}
\end{table}

Table \ref{table:questions} provides an example of an answered and unanswered question. All input fields in the table are as the user entered it.

@@

\subsection*{Variable Derivation}

\subsubsection*{Device Categorization}

Original device categories, defined by iFixit, included: Apparel, Appliance, Camera, Car and Truck, Computer Hardware, Electronics, Game Console, Household, Mac, Media Player, PC, Phone, Skills, Tablet, Vehicle. Device titles were parsed and certain categories were combined or separated to create a new device categorization. Categories in the final variable included: Android/Other Phone, Apple Product, Camera, Electronics, Game Console, Home, Other, PC, Tablet, Vehicle. Under original device categorization, 1,954 questions (25.2\% of 7,760) were not categorized correctly and indicated an NA for its category. Missing values were a result of users creating questions for devices not already in the iFixit's database, or from the user incorrectly defining the device name. For questions with missing categories, key words were searched for in device titles to recategorize accordingly.

\subsubsection*{Whether or not the question's title contains terms considered to by frequently-used among answered/unanswered questions}

@@

%Table with list of frequently used words
\begin{table}[!htbp]
\centering
\caption{Lists of ``frequently-used'' terms among answered and unanswered questions' titles, ordered by decreasing frequency}
\begin{tabular}{|p{4cm}|p{8cm}|}
  \hline
 ``Frequently-used'' terms among answered questions & screen, turn, working, replacement, power, work, replace, charging, charge, button, touch, black, turning, broken, start, stuck, new, lcd, upgrade, problem, change, port, replaced, card, open, boot, replacing, remove, reset, back, drive, error, cable, ssd, cracked, hard, one, dropped, logic, lines, white, keeps, pro, dead, now, front, damage, switch, parts, glass, still, charger, issue, sim, turns, digitizer, just, mode, model, backlight, usb, stopped, logo, starting, know, unresponsive, password, factory, call, use, damaged, find, sensor, possible, fixed, side, galaxy, data, ipod, problems, issue, slow, system, connector, without, overheating, code, ram, air, microphone, please, red, much, plugged, getting, booting, left, way, buy, plus, time, loose, lock, coming, got, shuts, says, install, key, door, top \\
  \hline
  ``Frequently-used'' terms among unanswered questions & sound, light, wifi, speaker, connect, picture, stay, noise, bluetooth, isnt, apps, going, rear, question, play, stop, service, take, hear, lights, showing, network, volume, come, keep, connection, flashing, shut, print, blue, buttons, edit \\ 
   \hline
\end{tabular}
\label{table:frequent_terms}
\end{table}

\subsubsection*{Whether or not the question's title ended in a questionmark}

@@

\subsubsection*{Whether or not the question's text contained at least one end punctuation mark}

>>>>

\makeatletter
\DeclareRobustCommand\bfseries{%
  \not@math@alphabet\bfseries\mathbf
  \fontseries\bfdefault\selectfont
  \boldmath % <-- added
}
\makeatother

@@

\section*{1. Introduction}

@@

\section*{2. Related Work}

@@

\section*{3. Materials}

% Table of categorical predictors
\begin{table}[!htbp]
\centering
\begin{tabular}{|p{10cm}|}
  \hline
  Day of the week the question was posted \\ \hline
  Device category the question pertains to. Categories include: Android\/Other Phone, Apple Products, Camera, Electronics, Game Console, Home, Other, PC, Tablet, Vehicle \\ \hline
  Whether or not the question's text contains any end punctuation marks (. ? !) \\ \hline
  Whether or not the question's text is in all lower case \\ \hline
  Whether or not the question's title contains at least one word that is considered ``frequently used'' among answered questions. See Appendix for a complete list of these terms. \\ \hline
  Whether or not the question's title contains at least one word that is considered ``frequently used'' among unanswered question. See Appendix for a complete list of these terms. \\ \hline
  Whether or not the question's title ends in a question mark \\ \hline
  Whether or not the user edited or added information to the question's text sometime after posting it. \\ \hline
  Whether or not the user made an effort to solve the problem prior to asking the question. \\ \hline
\end{tabular}
\caption{Categorical variables derived}
\label{table:categorical}
\end{table}

% Table of quantitative predictors
\begin{table}[!htbp]
\centering
\begin{tabular}{|p{10cm}|}
  \hline
  Average number of characters in each question's tags\\ \hline
  Average tag ``score'' for all of a question's tags. A tag score is defined as the proportion of times a tag appears in all of the data. Questions without tags were assigned a score of 0. \\ \hline
  Number of characters in the question's text \\ \hline
  Number of characters in the user-defined device name \\ \hline
  Ratio of the number of line breaks to the number of characters in the question's text \\ \hline
\end{tabular}
\caption{Continuous variables derived}
\label{table:continuous}
\end{table}

@@

\section*{4. Methods}

@@

In each fold of cross-validation, the full model was built on the training set and used to generate predicted hazard ratios on the corresponding test set. To assess prediction performance, predicted hazard ratios were entered into separate Cox models as the single quantitative predictor with response times as the survival time. The resulting Nagelkerke's R-square statistic, concordance statistic, Somers' \textit{Dxy}, partial likelihood ratio and p-value, were assessed as indicators of the model's performance \cite{Chen}. Signficant results from this model would indicate high predictive accuracy. The partial likelihood ratio assessed is a ratio of the log partial likelihood function evaluated at the parameter estimates, equivalent to a goodness of fit measure of the model with all predictors, and the log partial likelihood function for the null model with no predictors and only the baseline hazard function, equivalent to a goodness of fit measure for the null model. The p-value for this statistic was calculated from the $chi^2$ distribution \cite{find}. Concordance statistics and Somers' \textit{Dxy} are a measure of the model's discriminative ability. Concordance is defined as the probability that for any two randomly chosen questions, the question with the shorter response time also has the higher predicted hazard ratio. Concordance statistics close to 1 indicate high discriminative ability, while statistics close to 0.5 indicate discordance, or random predictions. Somers' \textit{Dxy} is the difference between the model's concordance statistic and discordance, 0.5. A Somers' \textit{Dxy} statistic of 0 indicates random predictions, while a statistic equal to 1 indicates perfect predictions \cite{Harrell2015}. These metrics were computed for each iteration on every training and test set. Averages of metrics across training and test sets were evaluated. The final model was then fit to the full data and the same metrics were computed and compared.

@@

\section*{5. Results}

@@

% Table of percentiles 
\begin{table}[!h]
\centering
\begin{tabular}{| l | l |}
  \hline
 \textbf{Percent Answered} & \textbf{Time (hrs)} \\ 
  \hline
  25 & 0.88 \\ 
  50 & 9.16 \\ 
  55 & 18.38 \\ 
  58 & 33.71 \\ 
  60 & 59.47 \\ 
  64 & 683.19 \\ 
   \hline
\end{tabular}
\caption{Kaplan-Meier estimated quantiles of survival time}
\label{table:quantiles}
\end{table}

@@

% Univariate analysis results
\begin{table}[!htbp]
\centering
\begin{tabular}{| p{5cm} | p{2.75cm} | p{2cm} |}
  \hline
  \textbf{Predictor} & \textbf{Transformation} & \textbf{p-value} \\ 
  \hline
  \multirow{ 3 }{ 5cm }{ Average frequency score of a question's tags }
  & Untransformed & 1.270620e-08 \\
  & Log + 1 & 1.186521e-08 \\
  & *Square root & 1.464184e-11 \\ \hline
  \multirow{ 3 }{ 5cm }{ Average number of characters in each question's tags }
  & Untransformed & 2.611529e-02 \\ 
  & *Log + 1 & 6.018542e-05 \\
  & Square root & 2.999917e-04 \\ \hline
  \multirow{ 3 }{ 5cm }{ Number of characters in a question's text }
  & Untransformed & 6.947221e-12 \\
  & *Log & 0.000000e+00 \\
  & Square root & 1.110223e-16 \\ \hline
  \multirow{ 3 }{ 5cm }{ Number of characters in the user-defined device title }
  & Untransformed & 6.530431e-03 \\
  & *Log + 1 & 1.912977e-05 \\
  & Square root & 2.291424e-04 \\ \hline
  \multirow{ 3 }{ 5cm }{ Ratio of the number of line breaks to the number of characters in a question's text } 
  & Untransformed & 1.398819e-07 \\
  & Log + 1 & 1.092952e-07 \\
  & *Square root & 1.148792e-11 \\ \hline
  \multicolumn{ 2 }{ |l| }{ *Day of the week the question was posted } & 7.867705e-04 \\ \hline
  \multicolumn{ 2 }{ |l| }{ *Device category } & 0.000000e+00 \\ \hline
  \multicolumn{ 2 }{ |p{7.75cm}| }{ *Whether or not the question's text contained at least one end punctuation mark } & 2.535394e-09 \\ \hline
  \multicolumn{2}{ |p{7.75cm}| }{ *Whether or not the question's text is in all lower case } & 1.540030e-07 \\ \hline
  \multicolumn{2}{| p{7.75cm}|}{ *Whether or not the question's title contains terms considered to be frequently used among answered questions } & 7.639738e-05 \\ \hline
  \multicolumn{2}{ |p{7.75cm}| }{ *Whether or not the question's title contains terms considered to be frequently used among answered questions } & 7.639738e-05 \\ \hline
  \multicolumn{2}{ |p{7.75cm}| }{ *Whether or not the question's title contains terms considered to be frequently used among unanswered questions } & 0.000000e+00 \\ \hline
  \multicolumn{2}{ |p{7.75cm}| }{ *Whether or not the question's title ended in a questionmark } & 1.142308e-12 \\ \hline
  \multicolumn{2}{ |p{7.75cm}| }{ *Whether or not the user edited or added information to the question's text sometime after posting it } & 2.547222e-07 \\ \hline
  \multicolumn{2}{ |p{7.75cm}| }{ *Whether or not the user had been a member for less than one day before the question was posted } & 0.000000e+00 \\ \hline
  \multicolumn{2}{ |p{7.75cm}| }{ *Whether or not the user made an effort to solve the problem on their own, prior to asking the question } & 3.164815e-05 \\ \hline
\end{tabular}
\caption{Univariate analysis results} 
\label{table:univariate_results}
\end{table}

@@

% Splines
\begin{table}[!htbp]
\centering
\begin{tabular}{| p{5cm} | l | l |}
  \hline
  \textbf{Predictor} & \textbf{K} & \textbf{AIC} \\ 
  \hline
  \multirow{ 4 }{ 5cm }{ Log transformation of the number of characters in a question's text } 
  & 0 & 65862.83 \\ 
  & \textbf{*}5 & 65862.02 \\ 
  & 4 & 65863.35 \\ 
  & 3 & 65862.08 \\ 
  \hline
  \multirow{ 4 }{ 5 cm }{ Square root transformation of the ratio of the number of line breaks to the number of characters in a question's text }
  & 0 & 65890.28 \\ 
  & 5 & 65884.70 \\ 
  & 4 & 65882.98 \\ 
  & \textbf{*}3 & 65881.93 \\ 
  \hline
  \multirow{ 4 }{ 5 cm }{ Square root transformation of the average frequency ``score'' of a question's tags }
  & \textbf{*}0 & 65890.75 \\ 
  & 5 & 65891.69 \\ 
  & 4 & 65891.75 \\ 
  & 3 & 65892.35 \\ 
  \hline
  \multirow{ 4 }{ 5 cm }{ Log transformation of the number of characters in the user-defined device title + 1 }
  & 0 & 65918.06 \\ 
  & \textbf{*}5 & 65847.34 \\ 
  & 4 & 65880.89 \\ 
  & 3 & 65898.00 \\ 
  \hline
  \multirow{ 4 }{ 5 cm }{ Log transformation of the average number of characters in a question's tags + 1 }
  & 0 & 65920.24 \\ 
  & 5 & 65911.20 \\ 
  & \textbf{*}4 & 65910.81 \\ 
  & 3 & 65914.98 \\ 
   \hline
\end{tabular}
\caption{Determining the optimal k number of splines for each predictor} 
\label{table:splines}
\end{table}

@@

% Cross-validation metrics
\begin{table}[!htbp]
\centering
\begin{tabular}{| r | r | r | r | r  | r | r | r |}
  \hline
 & \textbf{HR} & \textbf{LR} & \textbf{p-value} & \textbf{$R^2$} & \textbf{\textit{Dxy}} & \textbf{Concordance} \\ 
  \hline
  \textbf{Training Sets} & 2.015619 & 936.6705 & 0.0000 & 0.1400518 & 0.2691182 & 0.6345591 \\ 
  \textbf{Test Sets} & 1.975100 & 219.8065 & 0.0000 & 0.1400518 & 0.2579717 & 0.6289859 \\
  \textbf{Full Data} & 2.01843 & 1164.784 & 0.0000 & 0.1393817 & 0.2680962 & 0.6340481 \\ 
   \hline
\end{tabular}
\caption{Performance Metrics} 
\label{table:cv}
\end{table}

@@

% Final model on full data
\begin{table}[!htbp]
\centering
\begin{tabular}{|p{1.5cm}|p{6cm}|p{2.5cm}|p{2.5cm}|}
  \hline
 \textbf{Variable} & \textbf{Levels} & \textbf{Hazard Ratios} & \textbf{p-value} \\ 
  \hline
  \multirow{ 9 }{ 2 cm }{ Device Category } & Apple Product & 0.93 & \multirow{ 9 }{ 1.5cm }{ <0.0001 }\\ 
  & Camera & -0.26 & \\ 
  & Electronics & -0.08 &\\ 
  & Game Console & 0.21 &\\ 
  & Home & 0.39 &\\ 
  & Other & -0.11 &\\ 
  & PC & 0.43 &\\ 
  & Tablet & -0.15 &\\ 
  & Vehicle & 0.38 &\\
  \hline
  & Whether or not the user had been a member for less than one day before the question was posted & -0.10 & 0.0048 \\
  \hline
  & Whether or not the question's title contains terms considered to be frequently used among unanswered questions & -0.27 & <0.0001 \\ 
  \hline
  & Whether or not the question's title contains terms considered to be frequently used among answered questions & 0.05 & 0.2235\\ 
  \hline
  & Whether or not the question's title ended in a questionmark & 0.25 & <0.0001\\ 
  \hline
  & Whether or not the question's text contained at least one end punctuation mark & 0.03 & 0.5348\\ 
  \hline
  & Whether or not the question's text is in all lower case & -0.18 & 0.0052 \\ 
  \hline
  & Whether or not the user edited or added information to the question's text sometime after posting it & 0.28 & 0.0009 \\ 
  \hline
  & Whether or not the user made an effort to solve the problem on their own, prior to asking the question & -0.09 & 0.0137 \\ 
  \hline
  \multirow{ 6 }{ 2 cm }{ Day of the Week } & Monday & 0.01 & \multirow{ 6 }{ 1.5cm }{ 0.0004 }\\ 
  & Saturday & -0.07 & \\ 
  & Sunday & -0.11 & \\ 
  & Thursday & 0.03 & \\ 
  & Tuesday & 0.09 & \\ 
  & Wednesday & 0.10 & \\ 
  \hline
  & Square root transformation of the average frequency ``score'' of a question's tags & 2.23 & 0.0020 \\ 
  \hline
  \multirow{ 3 }{ 2cm }{ Square root transformation of the average number of characters in a question's tags } & _ & -0.08 & 0.0457\\ 
  & avg\_tag\_length' & 0.58 & Nonlinear \\ 
  & avg\_tag\_length'' & -1.52 & 0.0804\\ 
  \hline
  \multirow{ 4 }{ 2cm }{Log transformation of the number of characters in a question's text} & text length & -0.08 & 0.4344
  & text\_length' & -0.36 & Nonlinear \\ 
  & text\_length'' & 2.39 & 0.4578 \\
  & text\_length''' & -3.69 & \\ 
  \hline
  \multirow{ 4 }{ 2cm }{ Square root transformation of the number of characters in a question's device title} & device length & -0.07 & 0.2790 \\
  & device\_length' & 0.18 & Nonlinear \\ 
  & device\_length'' & -0.27 & 0.4185\\ 
  & device\_length''' & 0.21 & \\ 
  \hline
  \multirow{ 2 }{ 2cm }{ Square root transformation of the ratio of number of line breaks to number of characters in a question's text} & line break & 0.12 & 0.3569 \\
  & newline\_ratio' & 0.36 & Nonlinear: 0.6191 \\ 
   \hline
\end{tabular} 
\caption{Coefficients for predictors in the final model} 
\label{table:coefficients}
\end{table}

@@

\section*{6. Conclusion}

@@

The data analyzed for this model presented limitations, and may explain the model's low predictive accuracy. Many users on the CQA incorrectly specified the device name in their question (e.g. ``Turtle Beach Ear Force Xmy grandson chewed through the wire while he was playing it's brand-new is there anyway I can have it fixed0 One''), or did not include a device name at all. Many users also incorrectly used the tagging system by including ambiguous and lengthy tags like ``someone sat on it :('' or ``help me please!!!!!''(tags are generally a couple key words that describe the topic of the question). These inconsistencies in the data presented some difficulties in analysis, and may explain the model's low $R^2$ and discrimination indexes.

@@

\section*{7. Acknowledgement}

@@

\section*{8. Appendix}

% -----------------------------------------------------------
\subsection*{8.1 Posted questions}

% answered question id = 397414
% unanswered question id = 399971
% Table to display questions
\begin{table}[!htbp]
\centering
\begin{tabular}{| l | l | p{6cm} | l |}
  \hline
 \textbf{Answered} & \textbf{Device} & \textbf{Title} & \textbf{Date Posted} \\
  \hline
  Yes & iPhone 6 & iPhone water damage, touch screen issue &  2017-05-10 21:50:48 GMT \\ \cline{2 - 4}
  & \textbf{New User} & \textbf{Text} & \textbf{Date of First Answer} \\ \cline{2 - 4}
  & Yes & So I dropped my iPhone in water 4 days ago. Have done the whole rice thing and seen huge difference in it. However, only one side of my screen works and it is the one side which I need to unlock the phone. What would be the best way forward? & 2017-05-10 23:12:27 GMT \\ \cline{4 - 4}
  & & & \textbf{Response Time (hr)} \\ \cline{4 - 4}
  & & & 1.361 \\ \cline{4-4} \hline
  \textbf{Answered} & \textbf{Device} & \textbf{Title} & \textbf{Date Posted} \\ \cline{1 - 4}
  No & android tablet & ccccaaaan you help me fix my touch screen & 2017-05-23 07:35:12 GMT \\ \cline{2 - 4}
  & \textbf{New User} & \textbf{Text} & \textbf{Date of First Answer} \\ \cline{2 - 4}
  & No & touch screen not worki & NA \\ \cline{4 - 4}
  & & & \textbf{Response Time (hr)} \\ \cline{4 - 4}
  & & & NA \\ 
   \hline
\end{tabular}
\caption{Answered and unanswered questions}
\label{table:questions}
\end{table}

Table \ref{table:questions} provides an example of an answered and unanswered question. All fields in the table are shown as the user entered it.

@@

\subsection*{8.2 Variable Derivation}

\subsubsection*{8.2.1 Device Categorization}

Original device categories, defined by iFixit, included: Apparel, Appliance, Camera, Car and Truck, Computer Hardware, Electronics, Game Console, Household, Mac, Media Player, PC, Phone, Skills, Tablet, Vehicle. Device titles were parsed and certain categories were combined or separated to create a new device categorization variable to use in the Cox model. Categories created included: Android/Other Phone, Apple Product, Camera, Electronics, Game Console, Home, Other, PC, Tablet, Vehicle. Under the original device categorization, 1,954 questions (25.2\% of 7,760) were not categorized correctly and indicated an NA for its category. Missing values were a result of users creating questions for devices not already in the iFixit's database, or from the user incorrectly defining the device name. For questions with missing categories, key words were searched for in device titles to recategorize accordingly. All other questions with ambiguous device titles were categorized as Other.

\subsubsection*{8.2.2 Whether or not the question's title contains terms considered to by frequently-used among answered/unanswered questions}

@@

% Table with list of frequently used words
\begin{table}[!htbp]
\centering
\begin{tabular}{|p{4cm}|p{8cm}|}
  \hline
 \textbf{Frequently-used terms among answered questions} & screen, turn, working, replacement, power, work, replace, charging, charge, button, touch, black, turning, broken, start, stuck, new, lcd, upgrade, problem, change, port, replaced, card, open, boot, replacing, remove, reset, back, drive, error, cable, ssd, cracked, hard, one, dropped, logic, lines, white, keeps, pro, dead, now, front, damage, switch, parts, glass, still, charger, issue, sim, turns, digitizer, just, mode, model, backlight, usb, stopped, logo, starting, know, unresponsive, password, factory, call, use, damaged, find, sensor, possible, fixed, side, galaxy, data, ipod, problems, issue, slow, system, connector, without, overheating, code, ram, air, microphone, please, red, much, plugged, getting, booting, left, way, buy, plus, time, loose, lock, coming, got, shuts, says, install, key, door, top \\
  \hline
  \textbf{Frequently-used terms among unanswered questions} & sound, light, wifi, speaker, connect, picture, stay, noise, bluetooth, isnt, apps, going, rear, question, play, stop, service, take, hear, lights, showing, network, volume, come, keep, connection, flashing, shut, print, blue, buttons, edit \\ 
   \hline
\end{tabular}
\caption{Frequently-used terms among answered and unanswered questions' titles, ordered by decreasing frequency}
\label{table:frequent_terms}
\end{table}

\subsubsection*{8.2.3 Whether or not the question's title ended in a question mark}

@@

\subsubsection*{8.2.4 Whether or not the question's text contained at least one end punctuation mark}
